---
title: "introduction.Rmd"
author: "David Bian"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Binomial)
```

### Binomial 

The package "'Binomial'" is an implementation of a binomial distribution given a number
of trials and a probaiblity for success. There are several functions that can be used to
plot and summarize both the PDF and CDF of a binomial distribution.



### Creating a Binomial Random Variabe

Create a Binomial random variable using the bin_variable() function, which takes in a number of "trial" and the"probaiblity" of success. The function creates an object with and attribute "trial" and "probability" that you can use for other functions in the Binomial function.

```{r}
var <- bin_variable(20, .6)
var
var$trials
var$prob
```

### Summarizing a Binomial Random Variable

You can find key metrics of a Binomial object that you created from bin_variable() using the summary() function.

```{r}

summary(var)

```

### Finding a Binomial PMF or CDF

You can alternatively view a specific probability mass function of a binomial variable by using the bin_distribution() function. This function takes in two parameters "trial" and "prob" that work in the same way as the parameters for bin_variable(). You can either use the attributes of your Binomial object created from bin_variable() or you can manually input new values for the parameters. bin_distribution() will return an object that displays the Binomial PMF with your speciifed values. Alternatively, if you want to find the cummulative distribution function you can use the function bin_cummulative() which is identical to bin_distribution() in usage but outputs a CDF instead of a PMF.

```{r}
pdf_var <- bin_distribution(var$trials, var$prob)
pdf_var

cdf_var <- bin_cumulative(var$trials, var$prob)
cdf_var

```

### Plotting a Binomial Distribution

The Binomial package allows for easy visualization of a Binomial distribution. You can use the plot() function on an object created by the bin_distribution() or bin_cummulative() functions
to generate a plot.

```{r}
plot(pdf_var)
plot(cdf_var)
```

