---
output:
  github_document:
    html_preview: false
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

"'Binomial'" is a package that provides functions to simulate a binomial distribution

* `bin_choose(n, k)` calculates n choose k
* `bin_probability(s, t, p)` finds the probability of s successes in t trials with each success occuring with probability p
* `bin_distribution(t,p)` creates an object with class "bindis" that is a PMF for a binomial distribution with t trials and p probability for success.
* `bin_cumulative(t,p)` creates and object with class "bincum" that is a CDF for a binomial distribution with t trials and p probability for success.
* `plot()` method for a `bindis` or 'bincum' object that graphs the distribution.
* `bin_variable(t, p)` creates an object with class "binvar" with attributes "trials" with value t and "prob" with value p
* `summary()` method for a "binvar" object that gives key metrics for a given binomial random variable
* `bin_mean(t, p)` finds the mean of a binomial distribution with trials t and probability p
* `bin_variance(t, p)` finds the variance of a binomial distribution with trials t and probability p
* `bin_mode(t, p)` finds the mode of a binomial distribution with trials t and probability p
* `bin_skewness(t, p)` finds the skewness of a binomial distribution with trials t and probability p
* `bin_kurtosis(t, p)` finds the kurtosis of a binomial distribution with trials t and probability p


## Motivation

This package has been developed to make working with Binomial Distributions in R more convenient 


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("gastonstat/cointoss")
# install "cointoss" (with vignettes)
devtools::install_github("gastonstat/cointoss", build_vignettes = TRUE)
```


## Usage

```{r}
library(Binomial)

# 5 choose 3
bin_choose(5,3)

#Probability of 5 successes in 8 trials with probability of each success being .8
bin_probability(5, 8, .8)

#Create "bindis" and "bincum" objects with 10 trials and .7 probability of success
p <- bin_distribution(10, .7)
head(p)

c <- bin_cumulative(10, .7)
head(c)

#plotting "bindis" and "bincum" objects
plot(p)
plot(c)

#Create a "binvar" object with 20 trials and .8 probability of success
bin <- bin_variable(20, .8) 
bin

#summary statistics of "binvar" object
summary(bin)

#measures of a binomial distribution with 7 trials and .2 probability of success

bin_mean(7, .2)
bin_variance(7, .2)
bin_mode(7, .2)
bin_skewness(7, .2)
bin_kurtosis(7, .2)
```